---
title: "AssignmentProblem"
author: "Justin Charbonneau"
date: '2019-03-05'
output: html_document
---

# The solution

```{r warning=FALSE, message=FALSE}
library(tm)
library(SnowballC)
library(RColorBrewer)
library(wordcloud)
library(tidyverse)
```


```{r warning=FALSE, message=FALSE}
# Load the data

students <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/students.csv')
questions <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/questions.csv')
tags <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/tags.csv')
tag_users <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/tag_users.csv')
answers <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/answers.csv')
tag_questions <- read_csv('~/Desktop/Kaggle/D4G_CareerVillage/Data/tag_questions.csv')
```



## Issue

A common problem for the questions is that the hashtags related to the questions aren't matched with the professionals hashtags.

I will display this issue in a (question - professional) relationship.

Question id: __47f55e85ce944242a5a347ab85a8ffb4__

Professional id who answered this question: __4e9fe7ffb54c42eba0987c6119da9975__

Hashtag Word Cloud related to the question

Hashtag Word Cloud related to the professional

```{r}
tag_users <- tag_users %>%
  plyr::rename(.,c("tag_users_tag_id"="tags_tag_id"))

patterns <- c("#|-|!|@")

tag_users_full <- inner_join(tags,tag_users, by ='tags_tag_id') %>%
  mutate(tags_tag_name = str_replace_all(tags_tag_name, patterns,""),
         question_user = 'u')

tag_questions <- tag_questions %>%
  plyr::rename(.,c("tag_questions_tag_id"="tags_tag_id"))

tag_questions_full <- inner_join(tags,tag_questions, by ='tags_tag_id') %>%
  mutate(tags_tag_name = str_replace_all(tags_tag_name, patterns,""),
         question_user = 'q')
```

```{r}
tags_user_specific <- tag_users_full %>%
  filter(tag_users_user_id == '4e9fe7ffb54c42eba0987c6119da9975') %>%
  select(-tag_users_user_id)

tags_question_specific <- tag_questions_full %>%
  filter(tag_questions_question_id == '47f55e85ce944242a5a347ab85a8ffb4') %>%
  select(-tag_questions_question_id)





```

```{r}
par(mfrow=c(1,2))

tags_user_specific.Corpus<- Corpus(VectorSource(tags_user_specific$tags_tag_name))
wordcloud(words = tags_user_specific.Corpus,max.words=Inf,scale=c(1,1),random.color = TRUE,random.order=FALSE, colors=brewer.pal(8, "Dark2"))

tags_question_specific.Corpus<- Corpus(VectorSource(tags_question_specific$tags_tag_name))
wordcloud(words = tags_question_specific.Corpus,max.words=Inf,scale=c(1,1),random.color = TRUE,random.order=FALSE, colors=brewer.pal(8, "Dark2"))
```



```{r}
# Venn Diagram

library(grid)
library(futile.logger)
library(VennDiagram)
  
professional <- tags_user_specific$tags_tag_name

question <- tags_question_specific$tags_tag_name


overlap <- calculate.overlap(
  x = list(
    "Question" = question,
    "Professional" = professional
    )
  );

```

```{r}
grid.newpage();
venn.plot <- draw.pairwise.venn(length(overlap$a1),length(overlap$a2),length(overlap$a3),
                                category = c("Question Hashtags","Professional Hashtags"),
                                fill = c("dark blue", "orange"),
                                alpha = rep(0.5,2),
                                cat.pos = c(0,0),
                                fontfamily = "serif",
                                fontface = "plain",
                                lty = "blank")
grid.draw(venn.plot);
```

As you can see, they do not even have similar hashtags.

This is why we need to implement a better matching algorithm.

## Solution

As you whitnessed above, the assignment of the questions don't go to the correct professionals.

The proposed solution is simple, and effective. Also, it uses a library that is available in R.

We need to feed a matrix of student questions and professionals.

The rows will be the students questions, with ranking of which professionals can answer the question.

This ranking will be deternmined by the number of occurence of the hashtags from the questions and the hashtags of the professionals. If a professional follows (career, architecture and newyork) and the question contains career and architecture, then the value will be 2.

The hard part will be to calculate this matrix.

For every question, we need to calculate the number of occurence of the hashtag for each professional.

Let's dive in!

We have a data frame tag_questions that contains every question with it's respective hashtags.

tag_users contains both for the users and professionals. We would need to seperate the two, but for now, lets not for simplicity reasons.

### Dummy example

Note: We need a dummy data to fill in, as we need to have the same number of columns and rows for our matrix.

```{r}
question_hashtags <- tribble(
  ~question_id,~ hashtag,
  "q1", "datascience",
  "q1", "statistics",
  "q2", "architecture",
  "q2", "building",
  "q2", "newyork",
  "q3", "soccer",
  "q3", "scholarship",
  "dummy", ""
)

professionals_hashtags <- tribble(
  ~question_id,~ hashtag,
  "p1", "football",
  "p1", "sports",
  "p1", "soccer",
  "p2", "architect",
  "p2", "architecture",
  "p2", "washington",
  "p3", "career",
  "p3", "statistics",
  "p4", "datascience",
  "p4", "statistics"
)

```

Quickly see what my two data frames look like.

```{r}
View(question_hashtags)
View(professionals_hashtags)
```

To get the count, we will left_join.

```{r}
left_df <- left_join(question_hashtags,professionals_hashtags,by = "hashtag")
```

Get the count as a new data frame.

```{r}
cnts <- left_df %>%
  group_by(question_id.x,question_id.y) %>%
  summarise(.,n())
```

A bit more manipulation to get the perfect data frame.

```{r}
new_df <- cnts %>%
  spread(., key="question_id.y",value="n()")
```

```{r}
new_df_long <- new_df %>%
  gather(p1,p2,p3,p4,key="professional",value="count")
```

```{r}
max_counts_per_question <- new_df_long %>%
  group_by(question_id.x) %>%
  summarise(max_val = max(count, na.rm = TRUE))
```

```{r}
# Rejoin the max with the df.
new_df_long_max <- full_join(new_df_long,max_counts_per_question,by="question_id.x") %>%
  mutate(rank = max_val-count+1) %>%
  mutate(rank = ifelse(is.na(rank), 9, rank)) %>%
  select(question_id.x,professional,rank)

new_df_short_max <- new_df_long_max %>%
  spread(professional,rank)
```

### Solving the assignment problem

```{r}
library(lpSolve)

matrix_cols <- new_df_short_max[,-1]
m_temp <- as.matrix(sapply(matrix_cols, as.numeric))  

# Set col names and row names
col_name <- colnames(matrix_cols)
question_name <- pull(new_df_short_max, "question_id.x")

dimnames(m_temp)[[1]] <- question_name
dimnames(m_temp)[[2]] <- col_name

# View the cost ranked matrix
m_temp

fm <- lp.assign(m_temp)

# View the assigned matrix
fm$solution
```

Yooray! We have assigned the questions to the appropriate professionals. On of the professionals (p3) was assigned a dummy data, which means he wouldn't get any questions to answer.

## Next step is applying this to the real data








